Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support)\\ Technical Appendix Including Proofs and Details

### 2017-06-20 local-capability-machine/local-capability-machine.tex
updated TR with macro implementations (still missing call)

@@

              \subsection{Macro definitions}
              \begin{description}
              \item[\texttt{fetch} $r$ $f$] load the entry of the linking table corresponding to $f$ to register $r$.
              \item[\texttt{call} $r(\bar{r}_{\var{args}},\bar{r}_{\var{priv}})$] \forcenewline
                $\bar{r}_{\var{args}}$ and $\bar{r}_{\var{priv}}$ are lists of registers. An overview of this call:
                \begin{itemize}
                \item Set up activation record
                \item Create local enter capability for activation (protected return pointer)
                \item Clear unused registers
                \item Jump
                \item Upon return: Run activation code
                \end{itemize}
                A more detailed description of each of the above steps:
                \begin{description}
                \item [Set up activation record]\forcenewline
                  \begin{itemize}
                  \item Run malloc to get a piece of memory with space for:
                    \begin{itemize}
                    \item Words in $\bar{r}_{\var{priv}}$
                    \item Code return capability (opc)
                    \item Activation code
                    \end{itemize}
                  \item Store the words in $\bar{r}_{\var{priv}}$ to the activation record. 
                  \item Adjust a copy of the current pc to point to the return address in code and save it to the activation record.
                  \item Write the activation code to the activation record.
                  \end{itemize}
                \item [Create local enter capability for activation] Adjust the capability for the activation record to point to the beginning of the activation record and restrict it to a local enter-capability. Place this capability in $r_0$.
                \item [Clear unused registers]
                  Clear all the register that are not $\pcreg$, $r$, $r_0$ or in $\bar{r}_{\var{args}}$.
                \item [Jump] Jump to register $r$
                \item [Activation code] The activation code does the following:
                  \begin{itemize}
                  \item Move the stored ``private'' words in to their respective $\bar{r}_{\var{priv}}$ registers.
                    % \item Clear all registers but $r_1$, $\pcreg$, and $\bar{r}_{\var{priv}}$.
                  \item Load the return capability to $\pcreg$
                  \end{itemize}
                \end{description}
              \item[\texttt{malloc $r$ $n$}] Calls malloc to allocates a piece of memory of size $n$. The capability will be stored in register $r$. 
% Suggestion for malloc impl (r_t1 and r_t2 are registers in RegName_t), r_1 should not contain important stuff
% move r_1 n
% move r pc
% getb r_t1 r
% geta r_t2 r
% minus r_t1 r_t2 r_t1
% lea r r_t1
% move r_0 r_t1
% lea r_0 3 // 3 is offset to just after jmp
% restrict r_0 encodePerm(e)
% jmp r
% move r r_1
% move r_1 0
% move r_0 r_t1
% move r_t1 r_0

              \item[\texttt{assert$_{\var{flag}}$ $r_1$ $r_2$}] Compares the words in register $r_1$ and $r_2$ (if one of them is an integer, then use that in the comparison). If they are equal, then execution continues. If they are unequal, then the assertion flag named $\var{flag}$ in the flag list is set to 1 and execution halts (if no flag is specified, then the first flag in the list is set to 1).
              \item[\texttt{mclear $r$}] Stores 0 to all the memory cells the capability $r$ governs.\footnote{This may in some cases seem like an unreasonable slow instruction. In a real system it would probably be implemented as a vector operation which allows modification of continuous segments of memory rather fast.}
              \item[\texttt{rclear $\bar{r}$}] Moves 0 to all the registers in the list $\bar{r}$.
              \end{description}
              Note:
              \begin{itemize}
              \item \texttt{call} will fail if we have local capabilities in one of the registers of the ``private'' register list as it relies on a capability returned by malloc which will not be permit-write-local. This severely limits how \texttt{scall} can be used and it provides very little in terms of control-flow integrety when nested. Below, we introduce \texttt{scall} which can handle local capabilities in the ``private'' state. 
              \end{itemize}
              \subsection{Stack}
              Some programs will assume access to a stack which will be in part indicated by the program macros but also in the correctness lemma. The stack is accessed through a local $\rwlx$-capability. Programs will assume that the stack resides in some register, say $r_{\var{stk}}$.

@@

              \item[\texttt{push $r$}] Pushes the word in register \texttt{r} to the stack by incrementing the address of the stack capability by one and storing the word through the stack capability.
              \item[\texttt{pop $r$}] Pops the top word of the stack by loading it to register $r$, and decrementing the address of the stack capability.

@@

                  \end{itemize}\

@@

@@

%Possible implementation of crtcls \overline{(x,r_v)} r_code where |\overline{(x,r_v)}| = n (i_1,...,i_6 under)
% malloc r_t1 n
% store r_t1 r_v1
% lea r_t1 1
% store r_t1 r_v2
% lea r_t1 1
% ...
% lea r_t1 1
% store r_t1 r_vn
% lea r_t1 -n
% restrict r_t1 encodePerm(rw)
% malloc r_1 8 //length of activation record
% store r_1 r_code
% lea r_1 1
% store r_1 r_t1
% move r_t1 0
% lea r_1 1
% store r_1 encode(i_1)
% lea r_1 1
% store r_1 encode(i_2)
% lea r_1 1
% ...
% lea r_1 1
% store r_1 encode(i_6)
% lea r_1 -5 //offset to first instruction
% restrict r_1 encodePerm(e)

%Activation code (i_1,...,i_6)
% i_1 = move r_t1 pc
% i_2 = lea r_t1 -2
% i_3 = load r_env r_t1
% i_4 = lea r_t1 1
% i_5 = load r_t1 r_t1
% i_6 = jmp r_t1

              \item[\texttt{load $r$ $x$}] Assumes environment capability available in register $r_{\var{env}}$. Loads the word at the index associated with $x$ in the environment list. Loads from this capability into $r$.
              \item[\texttt{store $x$ $r$}] Assumes environment capability available in register $r_{\var{env}}$. Loads the word at the index associated with $x$ in the environment list. Stores the contents of register $r$ through this capability.
              \item[\texttt{reqglob $r$}] Tests if register $r$ contains a $\glob$ capability. If not fail, otherwise continue execution.
              \item[\texttt{reqperm $r$ $n$}] Tests if register $r$ contains a capability with permission $\decodePerm{n}$. If not fail, otherwise continue execution.
              \item[\texttt{prepstack} $r$] Tests if register $r$ contains a capability with permission $\rwlx$. If not fail, otherwise assume $r$ points to $((\rwlx,\gl),\start,\addrend,\addr)$ adjust it to $((\rwlx,\gl),\start,\addrend,\start - 1)$. 
                \lau{What if the stack starts at address 0? Changing the stack convention to always point at the first free cell will get rid of this problem (because our memory us uncapped.)}
              \item[\texttt{mclear $r$}] Clears all cells $r$ has authority over. 
              \item In a real setting due to a limited number of registers, some of the arguments might be spilled to the stack. It would be possible to do something similar here, but to keep
                matters simple, we opt not to do so.
              \item \texttt{reqperm} can be used to test whether something can pass as a stack.
              \item \texttt{reqglob} can be used to test whether a callback is admissible in the presence of a stack.
              \item The code of a closure will often be found in conjunction with the code that creates it.
              \item \texttt{prepstack} as ``prepare stack''. This ensures that the register contains something that looks like a stack and it is prepared for our stack convention.
                \label{fig:stack-before-call}
               & $\vdots$\\
               & 0 \\
                  $c_{\var{stk}} \rightarrow$   & local stack\\
               & $\vdots$\\
                \begin{tabular}{r | >{\centering\arraybackslash}p{0.75cm} |}
                  $\pcreg$ & $c_{\pc}$\\
                  $r_0$  & $c_0$ \\
                  $r_{\var{stk}}$  & $c_{\var{stk}}$ \\
                  $r_{\var{args},1}$ & $w_{a,1}$ \\
                  $r_{\var{args},n}$ & $w_{a,n}$\\
                  $r_{\var{priv},1}$ & $w_{p,1}$\\
                  $r_{\var{priv},m}$ & $w_{p,m}$\\
                \caption{This is the first figure of 6 that illustrates how \texttt{scall} works. In this example, the call \texttt{scall $r([r_{\var{args},1},\dots,r_{\var{args},n}],[r_0,r_{\var{priv},1},\dots,r_{\var{priv},m}])$. In this example the two lists of registers are disjoint even though that does not have to be the case.}}

@@

    \item $\reg'= \reg_0[\pcreg\mapsto\updatePcPerm{c_\adv},r_0 \mapsto c_{\mathit{ret}}, r_\stk \mapsto c_\stk, r_\adv \mapsto c_\adv]$ 

@@

      \item $\npair[n-k-1]{c_\adv} \in \stdvr{W}$ \\

@@

\subsection{Inverted Control and Return From Closure}
The following example is constructed to investigate the difficulties of preserving an adversary's local frame. There is no assertion as this is (slightly) beside the point. The lemma we would prove about this should look like Lemma~\ref{lem:correctness-g1}, but it is not state and proven here.
\begin{lstlisting}
g2:  move $\pcreg$ $r_3$
     lea $r_3$ $\dots$
     crtcls $[]$ $r_3$
     rclear $\RegName \setminus \{\pcreg,r_0,r_1 \}$
2g:  jmp $r_0$
f5:  reqglob $r1$
     prepstack $r_\stk$
     scall $r_1$($[]$,$[r_0,r_{\var{env}}]$)
     mclear $r_\stk$
     rclear $\RegName \setminus \{r_0,\pcreg\}$
5f:  jmp $r_0$
\end{lstlisting}

@@

Standard regions for when writing locally is permitted:
\begin{align*}
  &\iota^\pwl : \cal{P} \fun \Regions\\
  &\iota^\pwl\;A \defeq (\temp,1,=,=,H^\pwl \; S) \\
  \\
  &H^\pwl : \cal{P}(\Addrs) \fun \States \fun (\Wor \monwknefun \UPred{\HeapSegments})\\
  &H^\pwl\; A \; s \; \hat{W} \defeq \left\{\npair{\hs} \middle|
    \begin{aligned}
      &\dom(\hs) = A \land \\
      &\forall \addr \in A \ldotp \npair[n-1]{\hs(\addr)} \in \stdvr(\xi(\hat{W}))
    \end{aligned}
        \right\} \union \{\npair[0]{\ms} \}
\end{align*}
Revoking all temporary regions:
\begin{align*}
  \revokeTemp{} & : \Worlds \fun \Worlds \\
  \revokeTemp{W} & \defeq \lambda r \ldotp 
                   \begin{cases}
                     \revoked            & \text{if }W(r) = (\temp,s,\phi_\pub,\phi,H) \\
                     W(r)                & \text{otherwise}
                   \end{cases}
\end{align*}
Further define
\[
  \iota^\pwl_{\start,\addrend} \defeq \iota^\pwl([\start,\addrend])
\]

>>>>

\lau{Our instruction set could use a less than operator.}

@@

              \subsection{Macro definitions}
              \item[\texttt{fetch} $r$ $f$] load the entry of the linking table corresponding to $f$ to register $r$.\\
One possible malloc implementation (r\_t1 and r\_t2 are registers in RegName\_t).
\begin{lstlisting}
move r pc
getb r_t1 r
geta r_t2 r
minus r_t1 r_t1 r_t2 // Offset to first address, i.e., linking table (b-a)
lea r r_t1
load r r
lea r ... // ... replaced with offset to f in the linking table
move r_t1 0
move r_t2 0
load r r // f capability loaded to register r
\end{lstlisting}
              \item[\texttt{call} $r(\bar{r}_{\var{args}},\bar{r}_{\var{priv}})$] \forcenewline
                $\bar{r}_{\var{args}}$ and $\bar{r}_{\var{priv}}$ are lists of registers. An overview of this call:
                \item Set up activation record
                \item Create local enter capability for activation (protected return pointer)
                \item Upon return: Run activation code
                A more detailed description of each of the above steps:
                \item [Set up activation record]\forcenewline
                  \item Run malloc to get a piece of memory with space for:
                    \item Words in $\bar{r}_{\var{priv}}$
                    \item Code return capability (opc)
                    \item Activation code
                  \item Store the words in $\bar{r}_{\var{priv}}$ to the activation record. 
                  \item Adjust a copy of the current pc to point to the return address in code and save it to the activation record.
                  \item Write the activation code to the activation record.
                \item [Create local enter capability for activation] Adjust the capability for the activation record to point to the beginning of the activation record and restrict it to a local enter-capability. Place this capability in $r_0$.
                  Clear all the register that are not $\pcreg$, $r$, $r_0$ or in $\bar{r}_{\var{args}}$.
                \item [Jump] Jump to register $r$
                \item [Activation code] The activation code does the following:
                  \item Move the stored ``private'' words in to their respective $\bar{r}_{\var{priv}}$ registers.
                    % \item Clear all registers but $r_1$, $\pcreg$, and $\bar{r}_{\var{priv}}$.
                  \item Load the return capability to $\pcreg$
              \item[\texttt{malloc $r$ $n$}] Calls malloc to allocates a piece of memory of size $n$. The capability will be stored in register $r$. 
One possible malloc implementation (r\_t1 is a register in RegName\_t) and r\_1 is the register from the malloc specification.
\begin{lstlisting}
fetch r malloc
move r_1 n 
// save return pointer
move r_t1 r_0 
// setup new return pointer
move r_0 pc
lea r_0 4 // 4 is the offset to just after jmp r
restrict r_0 encodePerm(e)
jmp r
move r r_1
move r_0 r_t1 // restore return pointer
move r_1 0
move r_t1 0
\end{lstlisting}
              \item[\texttt{assert$_{\var{flag}}$ $r_1$ $r_2$}] Compares the words in register $r_1$ and $r_2$ (if one of them is an integer, then use that in the comparison). If they are equal, then execution continues. If they are unequal, then the assertion flag named $\var{flag}$ in the flag list is set to 1 and execution halts (if no flag is specified, then the first flag in the list is set to 1).\\
There are four different asserts based on whether $r_1$ and $r_2$ are registers or numbers. If $r_1$ and $r_2$ are registers:
\begin{lstlisting}
          // setup pointer to fail.
          move r_t3 pc
          lea r_t3 ... // ... is the offset to fail
          // make sure both registers contain either capability or integer
          isptr r_t1 r_1
          isptr r_t2 r_2
          minus r_t1 r_t1 r_t2
          jnz   r_t3 r_t1
          // set up capability for cap case:
          move r_t4 pc
          lea r_t4 ... // ... is the offset to caps
          jnz r_t4 r_t2 // jump to caps if r_t2 contains a capability
          // the two registers contain an integer
          minus r_t1 r_1 r_2
          jnz r_t3 r_t1
          // the two integers in the registers are equal
          move r_t4 pc
          lea r_t4 ... // .. offset to success
caps:
          geta r_t1 r_1
          geta r_t2 r_2
          minus r_t1 r_t1 r_t2
          jnz   r_t3 r_t1          
          getb r_t1 r_1
          getb r_t2 r_2
          minus r_t1 r_t1 r_t2
          jnz   r_t3 r_t1          
          gete r_t1 r_1
          gete r_t2 r_2
          minus r_t1 r_t1 r_t2
          jnz   r_t3 r_t1          
          getp r_t1 r_1
          getp r_t2 r_2
          minus r_t1 r_t1 r_t2
          jnz   r_t3 r_t1          
          getl r_t1 r_1
          getl r_t2 r_2
          minus r_t1 r_t1 r_t2
          jnz   r_t3 r_t1          
          // the two capabilities in the registers are equal
          move r_t4 pc
          lea r_t4 ... // .. offset to success
fail:
          // get the flag capability
          move r_t3 pc
          getb r_t1 pc
          geta r_t2 pc
          minus r_t1 r_t1 r_t2
          lea r_t3 r_t1
          lea r_t3 1 // the flag table capability is at the second address of cap.
          load r_t1 r_t3
          lea r_t1 ... // ... is the offset of flag in the table
          store r_t1 1
          halt
success:                   
          // clean up
          move r_t1 0
          move r_t2 0
          move r_t3 0
          move r_t4 0
\end{lstlisting}
If $r_1$ is a register, but $r_2$ is a constant:
\begin{lstlisting}
          // setup pointer to fail.
          move r_t3 pc
          lea r_t3 ... // ... is the offset to fail
          // make sure both registers contain either capability or integer
          isptr r_t1 r_1
          jnz   r_t3 r_t1
          minus r_t1 r_1 r_2
          jnz r_t3 r_t1
          // the two integers in the registers are equal
          move r_t3 pc
          lea r_t3 ... // .. offset to success
fail:
          // get the flag capability
          move r_t3 pc
          getb r_t1 pc
          geta r_t2 pc
          minus r_t1 r_t1 r_t2
          lea r_t3 r_t1
          lea r_t3 1 // the flag table capability is at the second address of cap.
          load r_t1 r_t3
          lea r_t1 ... // ... is the offset of flag in the table
          store r_t1 1
          halt
success:                   
          // clean up
          move r_t1 0
          move r_t3 0
\end{lstlisting}
The case where $r_1$ is a constant and $r_2$ is a register is omitted. The case where both are constant is also omitted - if the constants are the same, then the macro is nothing. If they are different, then it corresponds to the failed part of both of the above implementations.
              \item[\texttt{mclear $r$}] Stores 0 to all the memory cells the capability $r$ governs.\footnote{This may in some cases seem like an unreasonable slow instruction. In a real system it would probably be implemented as a vector operation which allows modification of continuous segments of memory rather fast.} \\
Possible implementation:
\begin{lstlisting}
        move r_t r
        getb r_t1 r_t
        geta r_t2 r_t
        minus r_t2 r_t1 r_t2
        lea r_t r_t2
        gete r_t2
        minus r_t1 r_t2 r_t1
        plus r_t1 r_t1 1
        move r_t2 pc
        lea r_t2 ... // ... is the offset to end
        move r_t3 pc
        lea r_t3 ... // ... is the offset to iter
iter:
        jnz r_t2 r_t1
        store r_t 0
        lea r_t 1
        plus r_t1 r_t1 1
        jmp r_t3
end:
        move r_t 0
        move r_t1 0
        move r_t2 0
        move r_t3 0
\end{lstlisting}
              \item[\texttt{rclear $\bar{r}$}] Moves 0 to all the registers in the list $\bar{r}$.\\
Possible implementation: Say $\bar{r} = r_1,\dots, r_n$
\begin{lstlisting}
move r_1 0
move r_2 0
// ...
move r_n 0
\end{lstlisting}

\end{description}
Note:
\begin{itemize}
\item \texttt{call} will fail if we have local capabilities in one of the registers of the ``private'' register list as it relies on a capability returned by malloc which will not be permit-write-local. This severely limits how \texttt{scall} can be used and it provides very little in terms of control-flow integrety when nested. Below, we introduce \texttt{scall} which can handle local capabilities in the ``private'' state. 
\end{itemize}
\subsection{Stack}
Some programs will assume access to a stack which will be in part indicated by the program macros but also in the correctness lemma. The stack is accessed through a local $\rwlx$-capability. Programs will assume that the stack resides in some register, say $r_{\var{stk}}$.

@@

\begin{description}
\item[\texttt{push $r$}] Pushes the word in register \texttt{r} to the stack by incrementing the address of the stack capability by one and storing the word through the stack capability.\\
Possible implementation:
\begin{lstlisting}
  lea r_stk 1
  store r_stk r
\end{lstlisting}

\item[\texttt{pop $r$}] Pops the top word of the stack by loading it to register $r$, and decrementing the address of the stack capability.
\begin{lstlisting}
  load r r_stk
  minus r_t1 0 1
  lea r_stk r_t1
\end{lstlisting}

@@

@@

Possible implementation, say $\bar{r}_{\var{args}} = r_{\var{args},1},\dots, r_{\var{args},m}$ and $\bar{r}_{\var{priv}} = r_{\var{priv},1},\dots, r_{\var{priv},n}$:
\begin{lstlisting}
// push private state
  push r_priv,1
  ...
  push r_priv,n
// push activation code
  push encode(i_1)
  ...
  push encode(i_4)
// push old pc
  move r_t1 pc
  lea r_t1 ... // ... is the offset to after
  push r_t1
// push stack pointer
  push r_stk
// set up protected return pointer
  move r_0 r_stk
  lea r_0 -5 // -5 is the offset to the first instruction of the activation code
  restrict r_0 encodePermPair((Local,e))
// restrict stack capability
  geta r_t1 r_stk
  plus r_t1 r_t1 1
  getb r_t2 r_stk
  subseg r_stk r_t1 r_t2
// clear unused part of the stack
  mclear r_stk
// clear non-argument registers
  rclear R // where R = RegisterName - {pc,r_stk,r_0,r,r_args}
  jmp r
after:
// pop the restore code
  pop r_t1
  pop r_t1
  pop r_t1
  pop r_t1
// pop the private state into approriate registers
  pop r_priv,1
  ...
  pop r_priv,n

\end{lstlisting}
where the restore code is as follows:
\begin{lstlisting}
 i_1 = move r_t1 pc
 i_2 = lea r_t1 5 // 5 is the offset to the address where the old stack pointer is located
 i_3 = load r_stk r_t1
 i_4 = pop pc
\end{lstlisting}

@@

Possible implementation of \texttt{crtcls $\overline{(x,r_v)}$ $r_{\var{code}}$} where $|\overline{(x,r_v)}| = n$ ($i_1$,...,$i_6$, i.e. the activation code, is defined later):
\begin{lstlisting}
malloc r_t1 n
store r_t1 r_v1
lea r_t1 1
store r_t1 r_v2
lea r_t1 1
...
lea r_t1 1
store r_t1 r_vn
lea r_t1 -n
restrict r_t1 encodePermPair((Global,rw))
malloc r_1 8 //length of activation record
store r_1 r_code // code capability
lea r_1 1
store r_1 r_t1 // environment capability
move r_t1 0
lea r_1 1
store r_1 encode(i_1)
lea r_1 1
store r_1 encode(i_2)
lea r_1 1
...
lea r_1 1
store r_1 encode(i_6)
lea r_1 -5 //offset to first instruction
restrict r_1 encodePerm(e)
\end{lstlisting}
Activation code ($i_1$,...,$i_6$):
\begin{lstlisting}
i_1 = move r_t1 pc
i_2 = lea r_t1 -2
i_3 = load r_env r_t1
i_4 = lea r_t1 1
i_5 = load r_t1 r_t1
i_6 = jmp r_t1
\end{lstlisting}

\item[\texttt{load $r$ $x$}] Assumes environment capability available in register $r_{\var{env}}$. Loads the word at the index associated with $x$ in the environment list. Loads from this capability into $r$.\\
Possible implementation:
\begin{lstlisting}
  move r_t1 r_env
  lea r_t1 ... // ... corresponds to offset of x in environment
  load r r_t1
  move r_t1 0
\end{lstlisting}
\item[\texttt{store $x$ $r$}] Assumes environment capability available in register $r_{\var{env}}$. Loads the word at the index associated with $x$ in the environment list. Stores the contents of register $r$ through this capability.
\begin{lstlisting}
  move r_t1 r_env
  lea r_t1 ... // ... corresponds to offset of x in environment
  store r_t1 r
  move r_t1 0
\end{lstlisting}
\item[\texttt{reqglob $r$}] Tests if register $r$ contains a $\glob$ capability. If not fail, otherwise continue execution.\\
Possible implementation:
\begin{lstlisting}
  getl r_t1 r
  minus r_t1 r_t1 encodeLoc(Global)
  move r_t2 pc
  lea r_t2 4 // 4 is the offset to just after fail
  jnz r_t1 r_t2
  fail
  move r_t1 0
  move r_t2 0
\end{lstlisting}
\item[\texttt{reqperm $r$ $n$}] Tests if register $r$ contains a capability with permission $\decodePerm{n}$. If not fail, otherwise continue execution.\\
Possible implementation:
\begin{lstlisting}
  getp r_t1 r
  minus r_t1 r_t1 n
  move r_t2 pc
  lea r_t2 4 // 4 is the offset to just after fail
  jnz r_t1 r_t2
  fail
  move r_t1 0
  move r_t2 0
\end{lstlisting}

\item[\texttt{prepstack} $r$] Tests if register $r$ contains a capability with permission $\rwlx$. If not fail, otherwise assume $r$ points to $((\rwlx,\gl),\start,\addrend,\addr)$ adjust it to $((\rwlx,\gl),\start,\addrend,\start - 1)$.\\
Possible implementation
\begin{lstlisting}
  reqperm r encodePerm(rwlx)
  getb r_t1 r
  geta r_t2 r
  minus r_t1 r_t1 r_t2
  lea r r_t1
  minus r_t1 0 1
  lea r r_t1
  move r_t1 0
  move r_t2 0
\end{lstlisting}
  \lau{What if the stack starts at address 0? Changing the stack convention to always point at the first free cell will get rid of this problem (because our memory us uncapped.)}\lau{Seeing as we did not change this: It does not give a problem as such because this would cause the machine to fail which is considered acceptable. It would also be possible to make a more ``sofisticated'' implementation that special cases on this and simply throws the first address away.}
\end{description}
Note:
\begin{itemize}
\item In a real setting due to a limited number of registers, some of the arguments might be spilled to the stack. It would be possible to do something similar here, but to keep
  matters simple, we opt not to do so.
\item \texttt{reqperm} can be used to test whether something can pass as a stack.
\item \texttt{reqglob} can be used to test whether a callback is admissible in the presence of a stack.
\item The code of a closure will often be found in conjunction with the code that creates it.
\item \texttt{prepstack} as ``prepare stack''. This ensures that the register contains something that looks like a stack and it is prepared for our stack convention.
\end{itemize}
\begin{figure}
  \label{fig:stack-before-call}
  \centering
  \begin{tabular}[!h]{r | >{\raggedright\arraybackslash}p{3cm} |}
    \multicolumn{2}{l}{Stack} \\
    \cline{2-2}
 & \\
 & $\vdots$\\
    \cline{2-2}
 & 0 \\
    \cline{2-2}
    $c_{\var{stk}} \rightarrow$   & local stack\\
 & $\vdots$\\
    \cline{2-2}
  \end{tabular}
  \hspace{1cm}
  \begin{tabular}{r | >{\centering\arraybackslash}p{0.75cm} |}
    \multicolumn{2}{r}{Register file} \\
    \cline{2-2}
    $\pcreg$ & $c_{\pc}$\\
    \cline{2-2}
    $r_0$  & $c_0$ \\
    \cline{2-2}
    $r_{\var{stk}}$  & $c_{\var{stk}}$ \\
    \cline{2-2}
    $r_{\var{args},1}$ & $w_{a,1}$ \\
    \cline{2-2}
             & $\vdots$ \\
    \cline{2-2}
    $r_{\var{args},n}$ & $w_{a,n}$\\
    \cline{2-2}
    $r_{\var{priv},1}$ & $w_{p,1}$\\
    \cline{2-2}
             & $\vdots$ \\
    \cline{2-2}
    $r_{\var{priv},m}$ & $w_{p,m}$\\
    \cline{2-2}
             & $\vdots$ \\
    \cline{2-2}
  \end{tabular}
  \caption{This is the first figure of 6 that illustrates how \texttt{scall} works. In this example, the call \texttt{scall $r([r_{\var{args},1},\dots,r_{\var{args},n}],[r_0,r_{\var{priv},1},\dots,r_{\var{priv},m}])$. In this example the two lists of registers are disjoint even though that does not have to be the case.}}
\end{figure}

@@

    \item $\reg'= \reg_0[\pcreg\mapsto\updatePcPerm{c_\adv},r_0 \mapsto c_{\mathit{ret}}, r_\stk \mapsto c_\stk', r_\adv \mapsto c_\adv]$ 

@@

      \item $\npair[n-k-1]{c_\adv} \in \stdvr(W)$ \\

@@

\subsection{Inverted Control and Return From Closure}
The following example is constructed to investigate the difficulties of preserving an adversary's local frame. There is no assertion as this is (slightly) beside the point. The lemma we would prove about this should look like Lemma~\ref{lem:correctness-g1}, but it is not state and proven here.
\begin{lstlisting}
g2:  move $r_3$ $\pcreg$
     lea $r_3$ $\dots$
     crtcls $[]$ $r_3$
     rclear $\RegName \setminus \{\pcreg,r_0,r_1 \}$
2g:  jmp $r_0$
f5:  reqglob $r1$
     prepstack $r_\stk$
     scall $r_1$($[]$,$[r_0,r_{\var{env}}]$)
     mclear $r_\stk$
     rclear $\RegName \setminus \{r_0,\pcreg\}$
5f:  jmp $r_0$
\end{lstlisting}

@@

Standard regions for when writing locally is permitted:
\begin{align*}
  &\iota^\pwl : \cal{P} \fun \Regions\\
  &\iota^\pwl\;A \defeq (\temp,1,=,=,H^\pwl \; A) \\
  \\
  &H^\pwl : \cal{P}(\Addrs) \fun \States \fun (\Wor \monwknefun \UPred{\HeapSegments})\\
  &H^\pwl\; A \; s \; \hat{W} \defeq \left\{\npair{\hs} \middle|
    \begin{aligned}
      &\dom(\hs) = A \land \\
      &\forall \addr \in A \ldotp \npair[n-1]{\hs(\addr)} \in \stdvr(\xi(\hat{W}))
    \end{aligned}
        \right\} \union \{\npair[0]{\ms} \}
\end{align*}
Revoking all temporary regions:
\begin{align*}
  \revokeTemp{} & : \Worlds \fun \Worlds \\
  \revokeTemp{W} & \defeq \lambda r \ldotp 
                   \begin{cases}
                     \revoked            & \text{if }W(r) = (\temp,s,\phi_\pub,\phi,H) \\
                     W(r)                & \text{otherwise}
                   \end{cases}
\end{align*}
Further define
\[
  \iota^\pwl_{\start,\addrend} \defeq \iota^\pwl([\start,\addrend])
\]
